% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.15in} % set width of text portion


\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Griffin Johnson}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{griffin@griff.la}
 \moveleft.5\hoffset\centerline{Pasadena, CA 91101}
 \moveleft.5\hoffset\centerline{(425) 417 - 5098}

\begin{resume}

\section{OBJECTIVE} Fullstack Engineer with 4+ years of experience seeking a full-time role as a Senior Software Engineer.

\section{EDUCATION} {\sl Bachelor of Science,} Computer Science\hfill  Graduated March 2020 \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                California Polytechnic State University, San Luis Obispo, CA 

\section{LANGUAGES \& FRAMEWORKS}
Javascript, Python, Kotlin, Swift, C, C++, Go, PHP, CSS, SCSS, PostgreSQL, NoSQL, Node.js, Deno, JQuery, React, Redux, Linux

\section{EXPERIENCE} 
	{\sl Fullstack Engineer} \hfill Fall 2020 - Present \\
	Supplyframe, Pasadena, Los Angeles, CA
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Worked on fullstack features for CPQ web applications. Worked closely with Product Managers to follow features from design through implementation.
		\item Worked full time on multiple concurrent projects, coordinating with engineers from both teams to meet deadlines and achieve project goals.
		\item Helped onboard new team members and provided guidance to get them up to speed quickly on the projects.
		\item Refactored application build processes to optimize bundling leading to decreased page loading times and improved responsiveness. Analyzed and refactored application SQL queries for memory and time complexity leading to faster execution times and a reduction in overall database load.
		\item Using PostgreSQL, Node.js, Express and EJS to server side render pages.
		\item Attended career fairs on behalf of the company and participated in technical interviews for new hires. 
	\end{itemize}
	
	{\sl Frontend Web Developer} \hfill Fall 2017 - Spring 2020 \\
	SkinnyKitchen.com, San Luis Obispo, CA
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Admin for Wordpress website. Managed communication with ad networks and hosting providers.
		\item Collaborated with owner to update UX and assets across the site.
	\end{itemize}
	
	{\sl CSC 436 Teaching Assistant} - Android, iOS \hfill Fall 2017 - Spring 2019 \\
	California Polytechnic State University, San Luis Obispo, CA
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Worked as a Teaching Assistant for the Mobile Application Development Course in both Android and iOS.
		\item Assisted students with lab assignments and coursework.
	\end{itemize}

\section{PROJECTS} 
    {\sl Plex Picks (plexpicks.griff.la)} - PostgreSQL, TypeScript \hfill            Fall 2024
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Fullstack web application to help groups vote for what movie to watch on Plex.
        \item Using Deno to connect groups of users and keep track of movie picks with live updates via web sockets.
    \end{itemize}
        
    {\sl Go YouTube Summarizer (Github griffinpj/goyts)} - Go, Javascript \hfill            Winter 2023
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Web application to summarize youtube videos with AI
        \item Using Whisper ASR for speech to text and Ollama for summarizing.
    \end{itemize}

    {\sl Portfolio Website (griffinjohnson.io)} - Rust, JavaScript \hfill            Summer 2020
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Lightweight portfolio site highlighting current and past projects.
        \item Using Rocket to serve html and a javascript bundle with redux to manage state.
    \end{itemize}
    
    {\sl Star Citizen LFG (Github Cougargriff/SCLFG)} - Firestore, Kotlin  \hfill            Spring 2020
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Android app that allows users to create and view group listings to find players online.
        \item Using Firebase for storage and authentication.

    \end{itemize}
				


\end{resume}
\end{document}===




